PyKE: Open source Python data analysis for NASA's Kepler, K2, and TESS missions

### 2018-01-18 paper/ms.tex
add example of how cbv correction improves k2 lightcurves

\documentclass{article}
\usepackage{amsmath, amssymb, bm}
\usepackage{bm}
\usepackage{graphicx, graphics}
\DeclareMathOperator*{\argmin}{arg\,min}

@@

In this setting, the user is left to choose the cost function and the number
of CBVs. It is often the case where $p=1$ yields robust (non-overfitted) results.
In fact, $p=1$ defines the $L_1$-norm which is robust against outliers [add reference].

@@

>>>>

\documentclass{article}
\usepackage{amsmath, amssymb, mathtools, bm}
\usepackage{graphicx, graphics}
\DeclareMathOperator*{\argmin}{arg\,min}

@@

In this setting, the user is left to choose the cost function and the number
of CBVs. It is often the case where $p=1$ yields robust (non-overfitted) results.
In fact, $p=1$ defines the $\ell_1$-norm which is robust against outliers [add reference].

@@

In the same fashion, we can apply cotrending basis vector correction to
\mathcal{K}\mathit{2} lightcurves.

For example, Fig.~\ref{fig:cbv-correction-k2} shows the result after estimating
the first nine coefficients for CBV correciton on target \texttt{EPIC 201543306}.
The selection of the number of CBVs is also done empirically by inspecting the
grid search curve.
\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.5]{figs/cbv-k2.pdf}
    \caption{CBV correction applied on \texttt{EPIC 201543306}.}
    \label{fig:cbv-correction-k2}
\end{figure}
